Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-16 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch 9 tables
Ch 9 comparison tables

An FDS model was developed to simulate the instrumented wall experiments with the natural gas burner.  Three different computational cell resolutions were examined to determine which resolution provided the best match to both the data from the instruments as well as the data from the fire patterns generated in the wall experiments.  The three computational grid sizes used were : 80~mm, 40~mm, and 20~mm.

@@

Instruments – FDS has devices, which are used to simulate thermocouples and total heat flux gauges.  This devices were positioned  in locations similar to the locations used in the physical experiments, in the plume region and on the wall.   A radiative heat flux gauge was also modelled to provide data at the 0.95 m from the centerline of the burner and 1.0 m above the top of the burner.  
In addition, FDS features devices that can not be implemented such as a device, which can be used to examine the heat release rate per unit length.  In this case, this device was used to determine flame height based on that measure.     
Fire 
The burner was modeled as an obstruction, with the same physical size as the burner.  It was modeled with a steady state heat release rate of 888.89 kW/m$^2$.   The chosen fuel reaction was `methane' since the majority <<<check percentage>> of the natural gas used in the laboratory experiments was methane.

@@

Compare Natural Gas at 0.61~m from instrumented wall and at 0.0~m from instrumented wall - problem bounds.

@@

@@

>>>>

An FDS model was developed to simulate the instrumented wall experiments with the natural gas burner.  One of the key determinations that is required when developing an FDS model is the mesh or grid cell size.  If a single plane of the data from the model were compared to a digital image we might refer to the grid cell size as the resolution of the image.  The smaller the grid cells the better the resolution. However increased resolution or the smaller grid cell size, the longer it will take the simulation to run.

For simulations involving buoyant plumes, a measure of how well the flow field is resolved is given by the non-dimensional expression $D^*/\dx$, where $D^*$ is a characteristic
fire diameter

\begin{equation}
 D^* = \left(
     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g} }
     \right)^\frac{2}{5} 
 \end{equation}

and $\dx$ is the nominal size of a mesh cell.

The characteristic fire diameter is related to the characteristic fire size via the
relation $Q^* = (D^*/D)^{5/2}$, where $D$ is the physical diameter of the
fire.}. The quantity, $\dQ$, is the total heat release rate of the fire. If it changes over time, you should consider the corresponding change in resolution. The quantity $D^*/\dx$ can be thought of as the number of computational cells spanning the characteristic (not necessarily the physical) diameter of the fire.

Three different computational cell resolutions were examined to determine which resolution provided the best match to both the data from the instruments as well as the data from the fire patterns generated in the wall experiments.  The three computational grid sizes used were : 80~mm, 40~mm, and 20~mm.

@@

Instruments – FDS has devices, which are used to simulate thermocouples and total heat flux gauges.  This devices were positioned  in locations similar to the locations used in the physical experiments, in the plume region and on the wall.   A radiative heat flux gauge was also modelled to provide data at the 0.95 m from the centerline of the burner and 1.0 m above the top of the burner.  
In addition, FDS features devices that can not be implemented such as a device, which can be used to examine the heat release rate per unit length.  In this case, this device was used to determine flame height based on that measure.     
Fire 
The burner was modeled as an obstruction, with the same physical size as the burner.  It was modeled with a steady state heat release rate of 888.89 kW/m$^2$.   The chosen fuel reaction was `methane' since the natural gas used in the laboratory experiments contained approximately 95~\% methane.

@@

In Chapter 2 the fires from the burners were characterized.  In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.  The average plume temperatures at elevations from 0.2~m through 2.2~ above the top face of the burner in 0.2~m increments will compared.  Two burner positions are examined, 0.61~m from the wall and 0.0~m from the instrumented gypsum wallboard wall.

@@

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 458						& 500					& 666 			& 620 	\\
		\hline 0.4			   & 738					   	& 819					& 761			& 527 	\\
		\hline 0.6			   & 632						& 769					& 643			& 385 	\\
		\hline 0.8			   & 442						& 600					& 522			& 198	\\
		\hline 1.0			   & 346						& 459 					& 402			& 151	\\
		\hline 1.2			   & 251						& 307 					& 284			& 119	\\
		\hline 1.4			   & 209						& 236 					& 213			& 98	\\
		\hline 1.6			   & 166						& 188 					& 164			& 86	\\
		\hline 1.8			   & 145						& 154 					& 133			& 76	\\
		\hline 2.0			   & 123						& 130 					& 112			& 69	\\
		\hline 2.2			   & 111						& 113 					& 99			& 61	\\
		\hline
	\end{tabular}
	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.61~m from the Wall]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
	\label{tab:FDSRI_Exp_Plume2d}
\end{table}

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 458						& 604					& 658 			& 667 	\\
		\hline 0.4			   & 751					   	& 824					& 793			& 643 	\\
		\hline 0.6			   & 668						& 711					& 673			& 577 	\\
		\hline 0.8			   & 519						& 575					& 581			& 353	\\
		\hline 1.0			   & 431						& 475 					& 506			& 357	\\
		\hline 1.2			   & 326						& 357 					& 406			& 306	\\
		\hline 1.4			   & 274						& 285 					& 322			& 233	\\
		\hline 1.6			   & 218						& 234 					& 257			& 201	\\
		\hline 1.8			   & 191						& 198 					& 211			& 179	\\
		\hline 2.0			   & 162						& 170 					& 178			& 150	\\
		\hline 2.2			   & 146						& 148 					& 153			& 140	\\
		\hline
	\end{tabular}
	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.0~m from the Wall.]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.0~m from the Wall.}
	\label{tab:FDSRI_Exp_Plume0d}
\end{table}

@@

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 458						& 500					& 666 			& 620 	\\
		\hline 0.4			   & 738					   	& 819					& 761			& 527 	\\
		\hline 0.6			   & 632						& 769					& 643			& 385 	\\
		\hline 0.8			   & 442						& 600					& 522			& 198	\\
		\hline 1.0			   & 346						& 459 					& 402			& 151	\\
		\hline 1.2			   & 251						& 307 					& 284			& 119	\\
		\hline 1.4			   & 209						& 236 					& 213			& 98	\\
		\hline 1.6			   & 166						& 188 					& 164			& 86	\\
		\hline 1.8			   & 145						& 154 					& 133			& 76	\\
		\hline 2.0			   & 123						& 130 					& 112			& 69	\\
		\hline 2.2			   & 111						& 113 					& 99			& 61	\\
		\hline
	\end{tabular}
	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
	\label{tab:FDSRI_Exp_Plume}
\end{table}
